Tournaments

### 2024-09-13 paper.qmd
Update paper.qmd
Adding blurb on graph theoretic tournaments.

>>>>

 Tournament (graphy theory): [wikipedia definition](https://en.wikipedia.org/wiki/Tournament_(graph_theory)) and in [McShane (2019)](https://scholar.smu.edu/hum_sci_statisticalscience_etds/13/) -- essentially a "round robin tournament" -- a graph where every node (competitor: A, B, C) is connected by a directed edge (win A -> B or lose A <- B), where there are no loops (self-directed edges -- competitors cannot play against themselves). AKA a complete directed graph with no loops; has $n$ nodes and $\choose{n}{2}$ edges. John W. Moon's [Topic on Tournaments](https://www.gutenberg.org/ebooks/42833) is the classic graph theoretical tournaments text. This definition should be used to disambiguate _tournament_, especially since graph theory may be used.
